Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-17 mu/article/article.tex
Adding alpha dependence in text for all formulae

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ (top frame, left scale) the
    corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame, right
    scale), the collinear (circled box) and perpendicular (square box) angles,
    and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
    structure fixing the energy to 0.912\,eV.}
    \label{fig:alt-vaz-rag}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ response is obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$ spectra resulting from evaluate
again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
polarization angle $\alpha$ for the \emph{alt} structure.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|$, related to the
left scale, fixing the energy of the incoming beam to 0.912\,eV for which value
the response is maximized for the \emph{alt} structure. In the same figure and
frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega)$ and in the bottom frame the corresponding
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yz}}(\omega)$
components. Again, the circled and square boxes indicate the values for which
the polarization angle and the velocity angle are parallel and perpendicular and
with arrows are indicated the corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ on the first Cartesian Quadrant of the
$xy$ plane. The circled box for the collinear angle corresponds for angles
$\alpha$ and $\gamma_{\mathrm{z}}(\omega)$ equal to $53.5^{\circ}$ with a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=12.7$\,Km/s, and the blue square
box indicates the perpendicular angles for values $\alpha=140^{\circ}$ and
$\gamma_{\mathrm{z}}(\omega)=50^{\circ}$ with a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega)|=43$\,Km/s. Finally we found that
for variations of $\pm0.5^{\circ}$ of those collinear and perpendicular angles,
presented with the error bars on the boxes, correspond ranges for the
polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and $95^{\circ} \leq
\alpha \leq 175^{\circ}$ covering a wide range of angles because the response
angle $\gamma_{\mathrm{z}}(\omega)$ has small variations for the complete range
of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of $|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega)|=27.1$\,Km/s
and $|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega)|=33.2$\,Km/s.

@@

Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
$|\mathcal{V}^{\mathrm{a}}|(\omega)$ response and made the analysis for the case
when the velocity is fixed in the $x$ and $y$ direction over the surface of the
\emph{alt} and \emph{up} structures. Also, using the Eqns. \eqref{eq:polar-ang}
and \eqref{eq:azimuthal-ang}, we determined the polar
$\theta_{\mathrm{a}}(\omega)$ and azimuthal $\varphi_{\mathrm{a}}(\omega)$
angles where the spin polarization is directed.

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ for \emph{up} structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ for \emph{up} structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The absolute maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega)|$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega)|$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

    \caption{Most intense response of
    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
    frames right scale), and the corresponding three components (bottom frames)
    for the \emph{up} structure fixing the polarization angle to
    $\alpha=40^{\circ}$ to maximize the response.}
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
presented in Fig. \ref{fig:up-3d-vva-1} and resulting from evaluate Eq.
\eqref{eq:vv-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab} for the \emph{up} structure.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega)$ and azimuthal $\varphi_{a}(\omega)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega)|$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
$\mathcal{V}^{\mathrm{xz}}(\omega)$, and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$
components.
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega)|$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The local maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ are localized in the energy range from
    1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
    $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}

    \caption{Intense response of
    $|\mathcal{V}^{\mathrm{x}}(\omega)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega)|$ (top frames left scale of Figs. (a) and
    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
    frames right scale), and the corresponding three components (bottom frames)
    for the \emph{up} structure fixing the polarization angle to
    $\alpha=40^{\circ}$ to maximize the response.}

@@

$\mathcal{V}^{\mathrm{xx}}(\omega)=-36.5$\,Km/s,
$\mathcal{V}^{\mathrm{xy}}(\omega)=-23.2$\,Km/s, and
$\mathcal{V}^{\mathrm{xz}}(\omega)= 39.8$\,Km/s 

@@

$|\mathcal{V}^{\mathrm{x}}(\omega)|=58.7$\,Km/s 

@@

$\theta_{\mathrm{x}}(\omega)=47$ and $\varphi_{\mathrm{x}}(\omega)=212$,
respectively, being directed upper the third Cartesian Quadrant of the $xy$
plane. Also from this figure we have that those angle values are hold for almost
all the peak of the response having a deviation of $\pm 2^{\circ}$ in the range
of energies from 0.028\,eV to 0.098\,eV from the corresponding to the absolute
maximum mentioned before.

@@

$\mathcal{V}^{\mathrm{yx}}(\omega)= -7.9$\,Km/s 
$\mathcal{V}^{\mathrm{yy}}(\omega)=  8.6$\,Km/s, and
$\mathcal{V}^{\mathrm{yz}}(\omega)= 87.2$\,Km/s 

@@

$|\mathcal{V}^{\mathrm{y}}(\omega)|=87.9$\,Km/s

@@

$|\mathcal{V}^{\mathrm{x}}(\omega)|$ To this absolute maximum correspond spin
polar and azimuthal angles $\theta_{\mathrm{y}}(\omega)=8$ and
$\varphi_{\mathrm{y}}(\omega)=133$, respectively, being directed almost

@@

Quadrant. In a different way than in the $|\mathcal{V}^{\mathrm{x}}(\omega)|$
case only the polar angle is hold for the peak of the response having a
deviation of $\pm 2^{\circ}$ since the onset to a energy value of 0.106\,eV but
the azimuthal angle changes since the onset to 0.106\,eV from $99^{\circ}$ to
$176^{\circ}$.

@@

We also found that since the onset of the response till an
energy for the incoming beam of 0.118\,eV the components of both,
$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
have no change in the spin polarization direction. Finally, after this energy
value both goes to zero.

@@

$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$
are obtained for the \emph{up} structure.

@@

$|\mathcal{V}^{\mathrm{x}}(\omega)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega)|$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized for the \emph{up} structure. In the same
figures and frames we present in dashed lines the corresponding polar
($\theta_{\mathrm{x}}(\omega)$ and $\theta_{\mathrm{y}}(\omega)$) and azimuthal
($\varphi_{\mathrm{x}}(\omega)$ and $\varphi_{\mathrm{y}}(\omega)$) angles
related to the right scale. In the bottom frames of same figures we present the
decomposition of the responses in the three corresponding components
$\mathcal{V}^{\mathrm{xx}}(\omega)$, $\mathcal{V}^{\mathrm{xy}}(\omega)$,
$\mathcal{V}^{\mathrm{xz}}(\omega)$ and $\mathcal{V}^{\mathrm{yx}}(\omega)$,
$\mathcal{V}^{\mathrm{yy}}(\omega)$, $\mathcal{V}^{\mathrm{yz}}(\omega)$. 

@@

in a value of $|\mathcal{V}^{\mathrm{x}}(\omega)|= 6.6$\,Km/s along the $x$
direction  with polar and azimuthal spin polarization angles
$\theta_{\mathrm{x}}(\omega)= 42^{\circ}$ and
$\varphi_{\mathrm{x}}(\omega)=59^{\circ}$ having fluctuations but being directed
over the first Cartesian Quadrant of the $xy$ plane.

@@

$|\mathcal{V}^{\mathrm{y}}(\omega)|=28.7$\,Km/s with polar and azimuthal angles
$\theta_{\mathrm{y}}(\omega)=45^{\circ}$ and
$\varphi_{\mathrm{y}}(\omega)=56^{\circ}$ having variations of $\pm5^{\circ}$
for energy variations of $\pm0.01$\,eV and being directed over the fir Cartesian

@@

$|\mathcal{V}^{\mathrm{x}}(\omega)|=9.9$\,Km/s and spin polarization angles
$\theta_{\mathrm{x}}(\omega)=129^{\circ}$ and
$\varphi_{\mathrm{x}}(\omega)=229^{\circ}$ being almost constant in the width of
the peak having variations of $\pm1^{\circ}$ for variations in energy of
$\pm0.01$\,eV and being directed downward the third Cartesian Quadrant of the

@@

$|\mathcal{V}^{\mathrm{y}}(\omega)|=49.4$\,Km/s with spin polarization angles
$\theta_{\mathrm{y}}(\omega)=127^{\circ}$ and
$\varphi_{\mathrm{y}}(\omega)=227^{\circ}$ being almost constant with variations

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-3d-svaz}
    \caption{$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, response
    vs. photon energy vs. polarization angle $\alpha$ for the \emph{alt}
    structure. The absolute maximum is located for an energy range from 0.90\,eV
    to 0.93\,eV and for polarization angles between $120^{\circ}$ and
    $150^{\circ}$.}
    \label{fig:alt-3d-vsb}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vaz-rag}
    \caption{Most intense response of
    $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ (top frame, left scale)
    the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega)$ (top frame,
    right scale), the collinear (circled box) and perpendicular (square box)
    angles, and the two components $\mathcal{V}^{\mathrm{xz}}(\omega)$ and
    $\mathcal{V}^{\mathrm{yz}}(\omega)$ (bottom frame) for the \emph{alt}
    structure fixing the energy to 0.912\,eV.}
    \label{fig:alt-vaz-rag}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained.
% 
In Fig. \ref{fig:alt-3d-vsb} we present the
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ spectra resulting from
evaluate again Eq. \eqref{eq:vs-mag} and Eq. \eqref{eq:vab} as a function of the
polarization angle $\alpha$ for the \emph{alt} structure.
% 
From this figure we found that the zone where the absolute maximum response is
held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
is obtained for the same polarization angles but for energies between 0.67\,eV
and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In the top frame of Fig. \ref{fig:alt-vaz-rag} we present in solid line the
result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related
to the left scale, fixing the energy of the incoming beam to 0.912\,eV for which
value the response is maximized for the \emph{alt} structure. In the same figure
and frame we present with dashed line, related to the right scale, the velocity
angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ and in the bottom frame the
corresponding $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ components. Again, the circled and
square boxes indicate the values for which the polarization angle and the
velocity angle are parallel and perpendicular and with arrows are indicated the
corresponding response value.
% 
From this figure and from Fig. \ref{fig:alt-3d-vsb} we have that the absolute
maximum response for the \emph{alt} structure is obtained for an incoming beam
with polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43.0$\,Km/s and for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane. The circled box for the collinear angle corresponds for
angles $\alpha$ and $\gamma_{\mathrm{z}}(\omega,\alpha)$ equal to $53.5^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=12.7$\,Km/s,
and the blue square box indicates the perpendicular angles for values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ with a
value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s. Finally
we found that for variations of $\pm0.5^{\circ}$ of those collinear and
perpendicular angles, presented with the error bars on the boxes, correspond
ranges for the polarization angle $30^{\circ} \leq \alpha \leq 70^{\circ}$ and
$95^{\circ} \leq \alpha \leq 175^{\circ}$ covering a wide range of angles
because the response angle $\gamma_{\mathrm{z}}(\omega,\alpha)$ has small
variations for the complete range of the polarization angle $\alpha$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the case when the spin polarization is directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

@@

Now, using the Eq. \eqref{eq:vv-mag}, we calculated the
$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response and made the analysis for
the case when the velocity is fixed in the $x$ and $y$ direction over the
surface of the \emph{alt} and \emph{up} structures. Also, using the Eqns.
\eqref{eq:polar-ang} and \eqref{eq:azimuthal-ang}, we determined the polar
$\theta_{\mathrm{a}}(\omega,\alpha)$ and azimuthal
$\varphi_{\mathrm{a}}(\omega,\alpha)$ angles where the spin polarization is
directed.

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for \emph{up}
    structure
    \label{fig:up-3d-vvx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ for \emph{up}
    structure
    \label{fig:up-3d-vvy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon
    energy vs. polarization angle for the \emph{up} structure. The absolute
    maxima of both responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy
    range from 0.08\,eV to 0.10\,eV and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ 
    \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ 
    \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}

    \caption{Most intense response of
    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs.
    (a) and (b)), the corresponding polar $\varphi$ and azimuthal $\theta$
    angles (top frames right scale), and the corresponding three components
    (bottom frames) for the \emph{up} structure fixing the polarization angle to
    $\alpha=40^{\circ}$ to maximize the response.}
    \label{fig:up-vab-comp-rtp-1}
\end{figure}

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ presented in Fig.
% 
\ref{fig:up-3d-vva-1} and resulting from evaluate Eq. \eqref{eq:vv-mag} as a
function of the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the
\emph{up} structure.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

In the top frames of  Figs. \ref{fig:up-vx-comp-rtp-1} and 
% 
\ref{fig:up-vy-comp-rtp-1} we present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$,
related to the left scale, fixing the polarization angle to $\alpha=40^{\circ}$
for which the response is maximized. In the same
figures and frames we present in dashed lines the corresponding polar
$\theta_{a}(\omega,\alpha)$ and azimuthal $\varphi_{a}(\omega,\alpha)$ angles related to the
right scale. Also, in the bottom frames of those figures we present the
decomposition of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ in the corresponding
$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and $\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$, $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
components.
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ for \emph{up} structure 
    \label{fig:up-3d-vvy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}

    \caption{$|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|$ response vs. photon energy vs.
    polarization angle for the \emph{up} structure. The local maxima of both
    responses $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are localized in the energy range from
    1.95\,eV to 2.00\,eV and for polarization angles from $25^{\circ}$ to
    $50^{\circ}$.}
    \label{fig:up-3d-vva-2}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}

    \caption{Intense response of
    $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ (top frames left scale of Figs. (a) and
    (b)), the corresponding polar $\varphi$ and azimuthal $\theta$ angles (top
    frames right scale), and the corresponding three components (bottom frames)
    for the \emph{up} structure fixing the polarization angle to
    $\alpha=40^{\circ}$ to maximize the response.}

@@

$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)=-36.5$\,Km/s,
$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)=-23.2$\,Km/s, and
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)= 39.8$\,Km/s 

@@

$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=58.7$\,Km/s 

@@

$\theta_{\mathrm{x}}(\omega,\alpha)=47$ and
$\varphi_{\mathrm{x}}(\omega,\alpha)=212$, respectively, being directed upper
the third Cartesian Quadrant of the $xy$ plane. Also from this figure we have
that those angle values are hold for almost all the peak of the response having
a deviation of $\pm 2^{\circ}$ in the range of energies from 0.028\,eV to
0.098\,eV from the corresponding to the absolute maximum mentioned before.

@@

$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)= -7.9$\,Km/s 
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)=  8.6$\,Km/s, and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)= 87.2$\,Km/s 

@@

$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=87.9$\,Km/s

@@

$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ To this absolute maximum correspond
spin polar and azimuthal angles $\theta_{\mathrm{y}}(\omega,\alpha)=8$ and
$\varphi_{\mathrm{y}}(\omega,\alpha)=133$, respectively, being directed almost

@@

Quadrant. In a different way than in the
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ case only the polar angle is hold
for the peak of the response having a deviation of $\pm 2^{\circ}$ since the
onset to a energy value of 0.106\,eV but the azimuthal angle changes since the
onset to 0.106\,eV from $99^{\circ}$ to $176^{\circ}$.

@@

We also found that since the onset of the response till an energy for the
incoming beam of 0.118\,eV the components of both,
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ have no change in the spin
polarization direction. Finally, after this energy value both goes to zero.

@@

$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ are obtained for the \emph{up}
structure.

@@

$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
the polarization angle to $\alpha=40^{\circ}$ for which the response is
maximized for the \emph{up} structure. In the same figures and frames we present
in dashed lines the corresponding polar ($\theta_{\mathrm{x}}(\omega,\alpha)$
and $\theta_{\mathrm{y}}(\omega,\alpha)$) and azimuthal
($\varphi_{\mathrm{x}}(\omega,\alpha)$ and
$\varphi_{\mathrm{y}}(\omega,\alpha)$) angles related to the right scale. In the
bottom frames of same figures we present the decomposition of the responses in
the three corresponding components $\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.

@@

in a value of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|= 6.6$\,Km/s along the
$x$ direction  with polar and azimuthal spin polarization angles
$\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and
$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ having fluctuations but being
directed over the first Cartesian Quadrant of the $xy$ plane.

@@

$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=28.7$\,Km/s with polar and azimuthal
angles $\theta_{\mathrm{y}}(\omega,\alpha)=45^{\circ}$ and
$\varphi_{\mathrm{y}}(\omega,\alpha)=56^{\circ}$ having variations of
$\pm5^{\circ}$ for energy variations of $\pm0.01$\,eV and being directed over
the fir Cartesian Quadrant of the $xy$ plane.

@@

$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|=9.9$\,Km/s and spin polarization
angles $\theta_{\mathrm{x}}(\omega,\alpha)=129^{\circ}$ and
$\varphi_{\mathrm{x}}(\omega,\alpha)=229^{\circ}$ being almost constant in the
width of the peak having variations of $\pm1^{\circ}$ for variations in energy
of $\pm0.01$\,eV and being directed downward the third Cartesian Quadrant of the

@@

$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|=49.4$\,Km/s with spin polarization
angles $\theta_{\mathrm{y}}(\omega,\alpha)=127^{\circ}$ and
$\varphi_{\mathrm{y}}(\omega,\alpha)=227^{\circ}$ being almost constant with
